---
title: "hw01-Soham-Ghosh"
output: github_document
---

## HW 01

```{r}
library(readr)
titles <- c("symboling", "normalized_losses", "make", "fuel_type", "aspiration", "num_of_doors", "body_style", "drive_wheels","engine_location","wheel_base","length","width","height","curb_weight","enginge_type", "num_of_cylinders","engine_size","fuel_system", "bore", "stroke","compression_ratio","horsepower","peak_rpm","city_mpg","highway_mpg","price")
types = c("double","double","character","character","character","character","character","character","character", "double","double","double","double","integer","character","character","integer","character","double","double","double","integer","integer","integer","integer","integer")
data <- read.csv(file = "imports-85.data", col.names = titles, colClasses = types, header = FALSE, na = "?")
data
str(data)
type_abbre <- "ddcccccccddddiccicdddiiiii"
data_alternate <- read_csv(file = "imports-85.data", col_types = type_abbre, na = "?", col_names = types)
data_alternate
```

### Technical Questions about importing data
<enter>
a. When you simply invoke the read.csv function on the data without making the vector of column names, the header becomes the first set of data points.
<enter>
b. The column vectors are named with the naming system of V#, from # being 1 and onward.
<enter>
c. If you don't specify how missing values are codified, an error occurs and the file can't be knit into a proper HTML.
<enter>
d. The second data type is bigger because you are specifying the amount of memory when defining the date type, whereas the first table does not have any limit or allocation when displaying the data.
<enter>
e. If you convert dat as an R matrix, it becomes a matrix of values.

###Practice base plotting
```{r}
hist(data$price, col= "blue")
boxplot(horizontal = TRUE, data$horsepower)
car_type <- as.data.frame(table(data$body_style))
car_type2 <- car_type[order(car_type$Freq, decreasing = TRUE),]
barplot(car_type2$Freq, axisnames = TRUE, names.arg = car_type2$Var)
aspiration_turbo = data[which(data$aspiration == "turbo"),]
turbo_table = stars(subset(aspiration_turbo, select = c("wheel_base", "length", "width", "height", "price")))
turbo_table
```
Histogram: The bars are blue, and it shows a clear trend that as prices of the cars increase, there is an apparent decrease in the quantity of those cars. There is a very high number of cars under the price of $10,000.
<enter>
Boxplot: The mean is a little below 100, and there are exactly 4 very high outliers.
<enter>
Barplot: The barplot is going is descending order, and the highest frequency of models is Sedan, while the lowest is covertible.
<enter>
The star plot shows that of the aspiration category of the data, which goes in increasing order from left to right and top to bottom. 

###Summaries
```{r}
data_gas = data[which(data$fuel_type == "gas"),]
data_diesel = data[which(data$fuel_type == "diesel"),]
mean_gas = mean(data_gas$price, na.rm = TRUE)
mean_diesel = mean(data_diesel$price, na.rm = TRUE)
mean_gas
mean_diesel
data_make = subset(data, select = c("make", "num_of_cylinders"))
cylinder_number = data_make[which(data_make$num_of_cylinders == "twelve"),]
cylinder_number
make_diesel = subset(data, select = c("make", "fuel_type"))
fuel = make_diesel[which(make_diesel$fuel_type == "diesel"),]
fuel2 = as.data.frame(table(fuel$make))
fuel2
hp = data[order(data$horsepower, decreasing=TRUE),]
hp[1,]["make"]
quantile(data$city_mpg, c(0.1))
quantile(data$highway_mpg, c(0.9))
bottom = data[which(data$city_mpg < 17),]
median(bottom$price, na.rm= TRUE)
```

The mean price of cars for gas is 12916.41 dollars and 15838.15 dollars for diesel.
<enter> 
The Jaguar has 12 cylinders.
<enter> 
Peugot has the most diesel cars.
<enter> 
The Porsche has the largest horsepower.
<enter> 
Bottom 10 percentile of MPG: less than 17 MPG.
<enter> 
Top 10 percentile of MPG: more than 38 MPG.
<enter> 
The median price for the lowest 10th percentile is $35550.

### Technical Questions about Data Frames
a. A 'NULL' output is returned.
```{r}
mtcars[["mpg"]]
mtcars$"mpg"
mtcars[ ,"mpg"]
```
b. The commands 2, 3, and 4 fail to return the vector mpg. 
c. The command fails to run because we have no referred to the variable.
d. Yes: you can include R list as a column of a data frame because the list is a valid datatype.
e. When you apply as.list as a data frame, it makes a list of column vectors from the data type.
f. It can be changed into a data framewith the command: data.frame().

### Correlations of quantitative variables
```{r}
removed_data <- subset(data, select = c("wheel_base","length","width","height","curb_weight","engine_size", "bore", "stroke","compression_ratio","horsepower","peak_rpm","city_mpg","highway_mpg","price"))
qdat = na.omit(removed_data)
qdat
if (!require('corrplot')) 
{
  install.packages('corrplot');
  library('corrplot');
}
plot_qdat <- cor(qdat)
corrplot(plot_qdat, method = "ellipse")
corrplot(plot_qdat, type = "upper", order = "hclust" )
```
The first correlation plot has ellipses within in of different sizes. The ellipses become significantly thinner when it is in the box of two of the same categories. For example, if it is in the box for length both on its top and to the left. Additionally, the data is normalized, and the positive correlation is in blue, with negative correlations being shown in red.
<enter> 
The second correlation plot has circles within it, which also is of different sizes and colors. Blue indicate a larger circle, and red circles are smaller. Any circle in a box with both categories as the same on the top and left are large blue circles. A bigger circle seems to indicate a higher value of r in absolute value. A large red circle indicates a high negative correlation. 
<enter> 

###Pricipal Components Analysis

```{r}
principal <- prcomp(scale = TRUE, qdat)
eigenvalues <- principal$sdev^2
eigenvalues
summary(principal)
scatter_vehicles <- principal$x
plot(scatter_vehicles[, "PC1"], scatter_vehicles[, "PC2"])

x <- principal$rotation[1:14]
y <- principal$rotation[15:28]
plot(x, y, type = 'n')
text(x,y, names(qdat), cex = 1.0, col = 'green')
arrows(0, 0, x, y, col = 'blue')

biplot(principal)
```

The plot has different lengths of the lines/arrows, which indicate different levels of correlation coefficient between the principal components and the variables. 
