---
title: "Introduction"
author: Soham Ghosh
date: 04/27/18
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to dieroller}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}

---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(dieroller)
```

## Die rolling

The package `"dieroller"` is a minimal implementation for simulating rolling
a die a given number of times, and to visualize the relative frequencies
in such a series of rolls.


## Creating a `die`

The first step is to create a `"die"` object with the function `die()`:

```{r}
mydie <- die()
mydie
```

By default, `die()` creates a _fair_ die with standard sides `heads`, and 
`tails`, and with probability values for each side of 0.5.

You can change the defatuls with arguments `sides` and `prob`:

```{r}
loaded <- die(sides = c(1,2,3,4,5,6), prob = c(1/12, 2/12,3/12,4/12,1/12,1/12))
loaded
```


## rolling a die

Once you have defined a `"die"` object, you can use the function `roll()` to
_roll_ a die a given number of `times`. The output will be an object of class 
`"roll"`, which will contain the vector of `rolls`:

```{r}
roll100 <- roll(mydie, times = 100)
roll100
```

The `summary()` function gives you a nice table of frequencies:
```{r}
summary(roll100)
```


## Plot of relative frequencies

You can use the function `plot()` to create a graohic with the relative 
frequencies of a series of die rolls:

```{r, fig.show='hold'}
plot(roll100)
```




